Bayesian inference of relative fitness on high-throughput pooled competition assays

### 2023-12-05 doc/_single_results.qmd
shorten discussion about Bayes vs Freq

---
editor:
    render-on-save: true
bibliography: references.bib
csl: ieee.csl
---

@@

The main advantage of our method is this natural interpretability of these
credible regions where an $X\%$ credible region indeed captures the region of
parameter space where we expect with $X\%$ probability the actual value of the
parameter lies given our statistical model, our prior information, and the
observed experimental data. A common mistake in the literature is interpreting
frequentist confidence intervals as Bayesian credible regions when they are not
equivalent [@morey2016]. Frequentist confidence intervals and Bayesian credible
regions are based on fundamentally different philosophical approaches to
statistics. Frequentist confidence intervals represent the range of values that
would contain the true population parameter with a certain probability if the
experiment was repeated many times. The confidence interval does not represent
the probability that the interval contains the true value. According to a
specific model and prior information, Bayesian credible regions represent the
range of values that contain the parameter with a certain posterior probability.
The credible region directly represents the probability that the region contains
the true value. So, frequentist confidence intervals cannot be interpreted as
Bayesian credible regions because they have fundamentally different meanings.
Treating an $X\%$ confidence interval like an $X\%$  credible region is
fallacious since confidence intervals do not represent probabilistic coverage of
the true value like credible regions. The intervals are generated through
entirely different procedures.

>>>>

---
editor:
    render-on-save: true
bibliography: references.bib
---

@@

The main advantage of our method is the natural interpretability of these
credible regions where an $X\%$ credible region indeed captures the region of
parameter space where we expect with $X\%$ probability the actual value of the
parameter lies given our statistical model, our prior information, and the
observed experimental data.
<span style="color: #912E27;">
Bayesian methods avoid common misconceptions associated with the construction of
frequentists confidence intervals [@morey2016].
</span>
